---
title: "Organic Seed Systems"
author: "Liza Wood"
year: "2023"
month: "September"
program: "ECOLOGY"
uccampus: "DAVIS"
report: "DISSERTATION"
degree: "DOCTOR OF PHILOSOPHY"
chair: "Mark Lubell"
signature1: "Tyler Scott"
signature2: "Neil McRoberts"
abstract: |
  "Overall abstract?"
acknowledgments: |
  "My acknowledgments"

knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
  aggiedown::thesis_pdf: 
    latex_engine: xelatex
bibliography: bib/thesis.bib
csl: csl/apsa.csl
link-citations: yes
linkcolor: "#31688EF"
urlcolor: "#482878FF"
citecolor: "#6DCD59F"
lot: true
lof: true
---



<!--chapter:end:index.Rmd-->

<!-- The {.unnumbered} option here means that the introduction will be "Chapter 0." You can also use {-} for no numbers on chapters. -->

# Introduction {-}

Short tying it all together

<!--chapter:end:00-intro.Rmd-->

```{r, child = '~/Documents/Davis/R-Projects/organicseed_adoption/ch1-manuscript/03_manuscript.Rmd'}
```


<!--chapter:end:01-chap1.Rmd-->

```{r, child = '~/Documents/Davis/R-Projects/osisn_spatial/ch2-manuscript/03_manuscript.Rmd'}
```


<!--chapter:end:02-chap2.Rmd-->

```{r, child = '~/Documents/Davis/R-Projects/osisn_processes/ch3-manuscript/03_manuscript.Rmd'}
```

<!--chapter:end:03-chap3.Rmd-->

# Conclusion {-}

If we don't want Conclusion to have a chapter number next to it, we can add the `{-}` attribute.

**More info**

And here's some other random info: the first paragraph after a chapter title or section head _shouldn't be_ indented, because indents are to tell the reader that you're starting a new paragraph. Since that's obvious after a chapter or section title, proper typesetting doesn't add an indent there.


<!--chapter:end:04-conclusion.Rmd-->

`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 


```{r, child = '~/Documents/Davis/R-Projects/organicseed_adoption/ch1-manuscript/04_appendix.Rmd'}
```

```{r, child = '~/Documents/Davis/R-Projects/osisn_spatial/ch2-manuscript/04_appendix.Rmd'}
```

```{r, child = '~/Documents/Davis/R-Projects/osisn_processes/ch3-manuscript/04_appendix.Rmd'}
```

<!--chapter:end:05-appendix.Rmd-->

# Colophon {-}

This document is set in [EB Garamond](https://github.com/georgd/EB-Garamond), [Source Code Pro](https://github.com/adobe-fonts/source-code-pro/) and [Lato](http://www.latofonts.com/lato-free-fonts/). The body text is set at 11pt with $\familydefault$. 

It was written in R Markdown and $\LaTeX$, and rendered into PDF using [aggiedown](https://github.com/ryanpeek/aggiedown) and [bookdown](https://github.com/rstudio/bookdown). 

This document was typeset using the XeTeX typesetting system, and the University of California Thesis class. Under the hood, the elements of the document formatting source code have been taken from the [Latex, Knitr, and RMarkdown templates for UC Berkeley's graduate thesis](https://github.com/stevenpollack/ucbthesis), and [Dissertate: a LaTeX dissertation template to support the production and typesetting of a PhD dissertation at Harvard, Princeton, and NYU](https://github.com/suchow/Dissertate)

The source files for this thesis have been compiled at https://github.com/liza-wood/aggiedown_dissertation. 


```{r echo = FALSE, eval = FALSE}
# I've set eval=FALSE to ensure Travis-CI can run
# if you're not using Travis-CI, then eval=TRUE will be fine
# library(git2r)
# if ( git2r::in_repository() ) {
#        summary(commits()[[1]]) 
# } else { 
#        message("We are not in a git repository") 
# }
```

<!---
The computational environment that was used to generate this version is as follows:

```{r echo = FALSE}
devtools::session_info()
```
--->

<!--chapter:end:98-colophon.Rmd-->


# References {-}

Placeholder



<!--chapter:end:99-references.Rmd-->

